Ship-based lidar evaluation of Southern Ocean clouds in the storm-resolving general circulation model ICON, and the ERA5 and MERRA-2 reanalyses

### 2024-12-13 manuscript_agu.tex
Fix citations

Our main finding corroborates previous findings of large boundary layer cloud biases in models and their subsequent effect on the radiative transfer. For example, low- and mid-level clouds in the cold-air sector of cyclones were identified as being responsible for most of the SW bias in \cite{bodas-salcedo2012}. This understanding was refined in \cite{bodas-salcedo2014}, which highlighted that the SW bias was associated with an incorrectly simulated mid-level cloud regime, which occurred in regions where cloud with tops at mid-level and low-levels occurred. Our results align less well with more recent work by \cite{ramadoss2024} which shows persistent shortwave radiative bias over the Southern Ocean are associated with incorrect cloud phase representation. While \cite{fiddes2024} suggest biases in the liquid water path are the largest contributor to the cloud radiative bias over the Southern Ocean. Our general finding applies to the new GSRM ICON, but the biases are generally lower than in the reanalyses, despite the reanalyses having the advantage of assimilation of the observed meteorological conditions. The GSRM has, on the other hand, the advantage of a much higher spatial resolution and, to a limited extent, explicit calculation of traditionally subgrid-scale processes such as convection.

>>>>

Our main finding corroborates previous findings of large boundary layer cloud biases in models and their subsequent effect on the radiative transfer. For example, low- and mid-level clouds in the cold-air sector of cyclones were identified as being responsible for most of the SW bias in \citeA{bodas-salcedo2012}. This understanding was refined in \citeA{bodas-salcedo2014}, which highlighted that the SW bias was associated with an incorrectly simulated mid-level cloud regime, which occurred in regions where cloud with tops at mid-level and low-levels occurred. Our results align less well with more recent work by \citeA{ramadoss2024} which shows persistent shortwave radiative bias over the Southern Ocean are associated with incorrect cloud phase representation. While \citeA{fiddes2024} suggest biases in the liquid water path are the largest contributor to the cloud radiative bias over the Southern Ocean. Our general finding applies to the new GSRM ICON, but the biases are generally lower than in the reanalyses, despite the reanalyses having the advantage of assimilation of the observed meteorological conditions. The GSRM has, on the other hand, the advantage of a much higher spatial resolution and, to a limited extent, explicit calculation of traditionally subgrid-scale processes such as convection.
